%-------------------------------------
% Resum in LaTeX (XeLaTeX)
% Author:  HF Yuan
% Project: https://github.com/xyz-yuanhf/yuan-resume
% Base on: https://github.com/mattyHerzig/mattys_resume
%          http://www.jianxu.net/en/
% License: MIT
%------------------------------------

\documentclass[a4paper, 10pt]{article}
\usepackage{myresume}  % Style package
\definecolor{highlightred}{HTML}{D4534A}  % Define custom red color
% --------------------  START  --------------------
\begin{document}

% -------------------- HEADING --------------------
\begin{flushright}
  \setstretch{0.6}
  \item {\Calluna (+61) 0413002799}  % Phone number
  \item {\Calluna linwei.tao@sydney.edu.au}  % E-mail address
  \item {\Calluna https://www.taolinwei.com}  % Home page
\end{flushright}\vspace{-45pt}

\begin{flushleft}  % Rplace here with your name (and identity if required)
  {\Calluna \fontsize{30pt}{30pt}\selectfont \textsc{Linwei Tao}} \quad {\Calluna \fontsize{10pt}{10pt}\selectfont{(Last updated: 25 Mar, 2026)}}
  \noindent\rule{\textwidth}{0.4pt}
    % \\\textcolor{highlightred}{PR Status: 189 visa score 85, last invitation round 70, close to invitation.}
\end{flushleft}

% -------------------- EDUCATION --------------------
\sectionBlock{
\section{Education}
}{
\eduHeading
  {School of Computer Science, University of Sydney}{Sydney, Australia}
  {Ph.D., Computer Science}{2023 - 2026 \footnotesize{\textit{(expected)}}}
\itemListStart
  \myItem{Advisors: Chang Xu \& Daochang Liu}
  \myItem{Research area: Uncertainty Calibration, Machine Learning}
\itemListEnd

\eduHeading
  {School of Computer Science, University of Sydney}{Sydney, Australia}
  {M.Phil., Computer Science}{2021 - 2023}
\itemListStart
  \myItem{Advisors: Chang Xu \& Lijun chang}
  \myItem{Research area: Uncertainty Calibration, Neural Architecture Search}
\itemListEnd

\eduHeading
  {School of Computer Science, University of Sydney}{Sydney, Australia}
  {M.E., Data Science}{2020 - 2021}
\newline
\newline
\eduHeading
  {Huazhong University of Science and Technology}{Wuhan, China}
  {B.E., Communication Engineering}{2013 - 2017}
\itemListStart
  \myItem{Received Science and Technology Scholarship}
\itemListEnd

}


% -------------------- EXPERIENCES --------------------
\sectionBlock{
\section{Experiences}
}{
\internHeading
  {Research Scientist Intern}{Google, Sydney}{2025.11 - 2026.02}
  \vfill
\internHeading
  {Teaching Assistant}{University of Sydney, Sydney}{2022 - now}
\itemListStart
  \myItem{COMP5329 Deep Learning  \hfill Spring 2022, 2023, 2024, 2025}
  \myItem{COMP5318 Machine Learning and Data Mining  \hfill Fall 2025}
  \myItem{HTIN5005 Applied Healthcare Data Science  \hfill Fall 2022, 2023}
  \myItem{OCMP5329 Deep Learning (Online)  \hfill Fall 2024, 2025}
  \myItem{BUSS6002 Data Science in Business  \hfill Spring 2024, 2025 Fall 2024, 2025}
  \myItem{QBUS5010 Intro to Dashboarding and Data Visualisation  \hfill Fall 2024, 2025}
\itemListEnd
\internHeading
  {Construction Supervisor}{Songjiang Construction Union, Shanghai}{2017.07 - 2019.10}
  \vfill
\internHeading
  {IOS Developer Intern}{Trip.com, Shanghai}{2015.06 - 2015.09}
  \vfill
\internHeading
  {Frontend Developer Intern}{Sunallies, Shanghai}{2014.06 - 2014.09}
}

% -------------------- AWARDS & HONORS --------------------
\sectionBlock{
\section{Awards\\and\\Grants}
}{
\awardListStart
\justifying
\item \emph{Apple Scholars in AI/ML PhD Fellowship}, Apple \hfill 2026.04
\item \emph{Cohere Labs Catalyst Grant} (\$1,000 USD), Cohere Labs \hfill 2026.04
\item \emph{SUPRA Social Impact Grant} (\$1,000 AUD), USYD \hfill 2026.04
\item \emph{FFT Student Survey Award for Outstanding Achievement in BUSS6002}, USYD Business School \hfill 2025.12
\item \emph{Faculty of Engineering HDR Grant} (\$1,000 AUD), USYD \hfill 2025.06
\item \emph{AAAI 2026 Student Program Committee} (3 selected worldwide), AAAI \hfill 2025.06
\item \emph{Google Cloud Research Credits Award (\$2340 AUD)}, Google \hfill 2024.05
\item \emph{International Tuition Fee Scholarship}, USYD \hfill 2023.06
\item \emph{Faculty of Engineering Research Support Scholarship}, USYD \hfill 2023.05
\item \emph{Excellent Student Cadre}, HUST, \hfill 2015.09
\item \emph{Science and Technology Scholarship}, HUST \hfill 2014.06
\awardListEnd
}

% -------------------- OTHERS --------------------
\sectionBlock{
\section{Academic Services}
}{
\skillListStart
\justifying
\item \emph{Conference Reviewer}: \textit{ICML, NeuIPS, ICLR, CVPR, ICCV, AAAI,  IJCAI, ACMMM, AISTATS}
\item \emph{Journal Reviewer}: \textit{T-MM, TMLR, DAMI, TPAMI, Machine Learning}
\skillListEnd
}
% -------------------- PUBLICATIONS --------------------
\sectionBlock{
\section{Publications}
}{
\pubListStart
\justifying
\item Xiaoyang Li, \textbf{Linwei Tao}, Haohui Lu, Minjing Dong, Junbin Gao, Chang Xu. Calibrating Graph Neural Networks with Wavelet-Aware Temperature Scaling. \textit{International Conference on Learning Representations, ICLR} 2026. 

\item Lei Pan, Zhipeng Lu, Yuan Zheng, Chongyao Yan, Haitao Wen, \textbf{Linwei Tao}, Chang Xu. Task-adaptive continual learning of vision language models via prototype routing and prompt. \textit{Neurocomputing}, 2026.

\item Haoyang Luo, \textbf{Linwei Tao}, Minjing Dong, Chang Xu. Beyond One-Hot Labels: Semantic Mixing for Model Calibration. \textit{International Conference on Machine Learning, ICML} 2025.

\item Jinxu Lin, \textbf{Linwei Tao}, Minjing Dong, Chang Xu. Uncertainty Weighted Gradients for Model Calibration. \textit{The IEEE / CVF Computer Vision and Pattern Recognition Conference, CVPR} 2025.

\item Jinxu Lin, \textbf{Linwei Tao}, Minjing Dong, Chang Xu. Diffusion Attribution Score: Evaluating Training Data Influence in Diffusion Model. \textit{International Conference on Learning Representations, ICLR} 2025. \textcolor{highlightred}{(Spotlight, 5.1\% of 11,500 submissions)}

\item \textbf{Linwei Tao}, Minjing Dong, Chang Xu. Feature Clipping for Uncertainty Calibration. \textit{AAAI Conference on Artificial Intelligence, AAAI }2025.

\item Lei Pan, Wuyang Luan, Yuan Zheng, Junhui Li, \textbf{Linwei Tao}, Chang Xu. GraphFusion: Integrating Multi-Level Semantic Information with Graph Computing for Enhanced 3D Instance Segmentation. \textit{Neurocomputing}, 2024.

\item \textbf{Linwei Tao}, Younan Zhu, Haolan Guo, Minjing Dong, Chang Xu. A Benchmark Study on Calibration. \textit{International Conference on Learning Representations, ICLR} 2024.

\item \textbf{Linwei Tao}, Minjing Dong, Chang Xu. Dual Focal Loss for Calibration. \textit{International Conference on Machine Learning, ICML} 2023.

\item \textbf{Linwei Tao}, Minjing Dong, Daochang Liu, Changming Sun, Chang Xu. Calibrating a Deep Neural Network with Its Predecessors. \textit{International Joint Conference on Artificial Intelligence, IJCAI} 2023.

\item \textbf{Linwei Tao}, Yi-Fan Yeh, Minjing Dong, Tao Huang, Philip Torr, Chang Xu. Revisiting Uncertainty Estimation and Calibration of Large Language Models. \textit{Conference on Neural Information Processing Systems, NeurIPS} 2025 Scaling Environments for Agents (SEA) Workshop

\item Yingqing Yuan, \textbf{Linwei Tao}, Haohui Lu, Matloob Khushi, Imran Razzak, Mark Dras, Jian Yang, Usman Naseem. KG-UQ: Knowledge Graph-Based Uncertainty Quantification for Long Text in Large Language Models. \textit{International World Wide Web Conference, WWW} 2025 Workshop on Sustainable AI for the Future Web
\pubListEnd
}


% -------------------- PREPRINTS --------------------
\sectionBlock{
\section{Preprints}
}{
\pubListStart
\justifying
\item \textbf{Linwei Tao}, Haoyang Luo, Minjing Dong, Chang Xu. Confidence Calibration under Ambiguous Ground Truth. \textit{arXiv:2603.22879}, 2026.

\item \textbf{Linwei Tao}, Yi-Fan Yeh, Bo Kai, Minjing Dong, Tao Huang, Tom A. Lamb, Jialin Yu, Philip H.S. Torr, Chang Xu. Can Large Language Models Express Uncertainty Like Human?
\item Haolan Guo, \textbf{Linwei Tao}, Haoyang Luo, Minjing Dong, Chang Xu. Sample Margin-Aware Recalibration of Temperature Scaling
\item \textbf{Linwei Tao}, Haolan Guo, Minjing Dong, Chang Xu. Consistency Calibration: Improving Uncertainty Calibration via Consistency among Perturbed Neighbors.
\item Yunke Wang, \textbf{Linwei Tao}, Bo Du, Yutian Lin, Chang Xu. Visual Imitation Learning with Calibrated Contrastive Representation.
\item Younan Zhu, \textbf{Linwei Tao}, Minjing Dong, Chang Xu. Attention Calibration for Reducing Hallucination in Large Vision-Language Models.
\pubListEnd
}



% % -------------------- TALKS --------------------
% \sectionBlock{
% \section{Talks}
% }{
% \talkListStart
% \justifying
% \item “ITCD: Image to Text Translation for Classification by Diffusion Models”, at Efficiency, Security, and Generalization of Multimedia Foundation Models Workshop @ ACM Multimedia 2024 \hfill 2024.10
% \item “Dual Focal Loss for Calibration”, at AI-Time \hfill 2023.05
% \item “Calibrating a Deep Neural Network with Its Predecessors”, at University of Sydney, Deep Learning class \hfill 2023.02
% \talkListEnd
% }



\end{document}